\setcounter{section}{0}
\renewcommand{\thesection}{\Alph{section}}
\numberwithin{equation}{section}

\section{Derivation of self-recapture ``the other way round''}

As discussed in Section \ref{subsec:selfPs}, \eqref{eq:self-staged}
can also be formulated \textquotedbl the other way round\textquotedbl ,
i.e., considering whether the second sample is the same as the first.
The answer turns out the same, but the derivation is slightly different
and \emph{appears} to involve an explicit survival term. Again, suppose
two female samples ($y_{1},a_{1}$ and $y_{2},a_{2}$ , where $y_{1}<y_{2}$),
then 
\begin{gather*}
\mathbb{P}\left[K_{21}=\text{SP}\vert y_{1},a_{1},y_{2},a_{2}\right]\\
=\frac{\mathbb{P}\left[\text{Sample 1 survived until Sample 2 was taken}\right]\mathbb{I}\left(y_{2}-a_{2}=y_{1}-a_{1}\right)}{N\left(y_{2},a_{2}\right)}\\
=\frac{\Phi\left(y_{2}-y_{1},a_{1}\right)\mathbb{I}\left(y_{2}-a_{2}=y_{1}-a_{1}\right)}{N\left(y_{2},a_{2}\right)}.
\end{gather*}

However, the results are readily seen to be identical because, by
definition of \textquotedbl survival\textquotedbl , we have
\begin{gather}
N\left(y+t,a+t\right)\equiv N\left(y,a\right)\Phi\left(t,a\right).\label{eq:cons-of-nums}
\end{gather}

\pagebreak{}

\section{Self-recapture when exact age is known\label{subsec:selfP-exact-age}}

\citet{beatty_estimating_2022} used a fairly complex IMR formulation
to cope with historically-very-imprecise estimates of age (or, more
realistically, of \textquotedbl stage\textquotedbl ) estimates.
However, when accurate age data are available, the pairwise comparison
probabilities for self-recapture are remarkably simple. Suppose two
female samples ($y_{1},a_{1}$ and $y_{2},a_{2}$ , where $y_{1}<y_{2}$).
Then the probability that the first one is the same as the second
is just
\begin{gather}
\mathbb{P}\left[K_{12}=\text{SP}\vert y_{1},a_{1},y_{2},a_{2}\right]=\frac{\mathbb{I}\left(y_{2}-a_{2}=y_{1}-a_{1}\right)}{N_{y_{1},a_{1}}}.\label{eq:SP}
\end{gather}
The indicator $\mathbb{I}\left(\cdot\right)$ is 1 if the two samples
were born in the same year, or 0 if not, The samples can only be from
the same animal if they were both born in the same year and if they
were, we then need to know how many females of age $a_{1}$ were alive
at $y_{1}$, $N_{y_{1},a_{1}}$. This implicitly assumes that all
females of the same age have the same survival and sampling probabilities.
(See appendix for the equivalent derivation of $\mathbb{P}\left[K_{21}=\text{SP}\vert y_{1},a_{1},y_{2},a_{2}\right]$).

In principle, given unlimited data, we could separately apply \eqref{eq:SP}
to each combination of $\left(y,a\right)$-consistent pairs, to empirically
estimate from all numbers-at-age-and-year from the reciprocal of the
observed rates. Then we could apply \eqref{eq:cons-of-nums} to estimate
year-and-age-specific survivals. In practice, that would be ridiculous,
since it would require an enormous number of recaptures and would
lead to noisy abundance estimates, estimated survivals greater than
one, and so on. However, the principle does illustrate the great power
of \emph{known-age} mark-recapture data. Note also that there are
no assumptions about equiprobable sampling across ages, etc; all probabilities
are simply conditioned on observed ages, and it does not particularly
matter \emph{why} there are more samples of one age than another.

The big problem with applying \eqref{eq:SP} in an ICKMR setting,
i.e., with conditioning on age explicitly, is that it requires explicit
calculation of all $N_{y_{1},a_{1}}$ within the model. This is normally
unnecessary with CKMR for mammal-like species, where the main information
is \emph{only} connected with aggregate adult abundance (via TRO).
It is extremely convenient to work just with a \textquotedbl homogenous
block\textquotedbl{} of adults, and there is in any case no direct
information on population age composition unless extra data are used.
One option is \textquotedbl just\textquotedbl{} to work with a fully-age-structured
population dynamics framework— but that is a lot of work to develop
(from experience in fisheries work) and requires modelling extra data.\pagebreak{}

\section{Derivation of juvenile abundance\label{sec:Deriv-Njy}}

The key point here is that we don't need to decompose the adult stage
into separate age classes.

Following notation from the rest of the paper, let the number of adults
in year $y$ be $N_{\text{A},t}$ where adulthood means being aged
$\alpha$ or older. The number next year will be $\rho N_{\text{A},y+1}$
where $\rho=e^{r}$ and $r$ is the rate of increase as in \eqref{popdyn}.
That will be made up of survivors from adults at $t$, plus survivors
from the incoming cohort of oldest juveniles, aged $\alpha-1$. Thus
\begin{gather}
N_{y+1,\text{A}}=\rho N_{y,\text{A}}=\phi_{\text{A}}N_{y,\text{A}}+\phi_{\text{J}}N_{y,\alpha-1}.\label{eq:mvb-nj-1}
\end{gather}
Rearranging, we have
\begin{gather}
N_{y,\alpha-1}=\frac{\rho-\phi_{\text{A}}}{\phi_{\text{J}}}N_{y,\text{A}}.\label{eq:mvb-nj-final-juve}
\end{gather}
We now need to infer the numbers in the other juvenile age-classes
(not just $\alpha-1$). Starting with the penultimate juvenile age-class,
we have: 
\begin{align*}
N_{y,\alpha-1} & =\phi_{\text{J}}N_{y-1,\alpha-2} & \text{ (survival)}\\
N_{y,\alpha-1} & =\rho N_{y-1,\alpha-1} & \text{ (population growth)}\\
\implies N_{y,\alpha-2} & =\frac{\rho}{\phi_{\text{J}}}N_{y,\alpha-1}.
\end{align*}
Similar relationships apply to each preceding juvenile age class,
down to age 1. The total number of juveniles in year $y$, $N_{y,\text{J}}$,
is given by a sum from age $x=\alpha-1$ down to age 1:
\begin{align}
N_{y,\text{J}}=\sum_{x=1}^{\alpha-1}N_{y,\alpha-x} & =\sum_{x=1}^{\alpha-1}N_{y,\alpha-1}\left(\frac{\rho}{\phi_{\text{J}}}\right)^{x-1}\nonumber \\
 & =N_{y,\alpha-1}\sum_{x'=0}^{\alpha-2}\left(\frac{\rho}{\phi_{\text{J}}}\right)^{x'}\nonumber \\
 & =N_{y,\alpha-1}\frac{1-\left(\rho/\phi_{\text{J}}\right)^{\alpha-1}}{1-\rho/\phi_{\text{J}}},\label{eq:mvb-nj-totjuve}
\end{align}
using the standard result for a geometric series: $\sum_{i=1}^{n}ar^{i}=a\frac{1-r^{n}}{1-r}$.
Substituting for $N_{t,\alpha-1}$ from \eqref{eq:mvb-nj-final-juve},
we have
\begin{align*}
N_{y,\text{J}} & =N_{y,\text{A}}\frac{\rho-\phi_{\text{A}}}{\phi_{\text{J}}}\frac{1-\left(\frac{\rho}{\phi_{\text{J}}}\right)^{\alpha-1}}{1-\frac{\rho}{\phi_{\text{J}}}}\\
 & =N_{y,\text{A}}\frac{\rho-\phi_{\text{A}}}{\rho-\phi_{\text{J}}}\left(\left(\frac{\rho}{\phi_{\text{J}}}\right)^{\alpha-1}-1\right).
\end{align*}
Now, for the case of walrus, we know that $\alpha=6$, so:
\begin{align*}
N_{y,\text{J}} & =N_{y,\text{A}}\frac{\rho-\phi_{\text{A}}}{\rho-\phi_{\text{J}}}\left(\left(\frac{\rho}{\phi_{\text{J}}}\right)^{5}-1\right).
\end{align*}
\pagebreak{}

\section{Further HSP complications}

The second issue with all second-order kin, is that pairwise-kinship
statistics are not currently powerful enough to completely distinguish
them all from a few ``lucky'' third-order kin such as Great-Gandparent-Grandchild.
To handle this without bias, the best approach is set a threshold
for the statistic that should almost completely exclude false-positives
from third-order kin, then to estimate empirically the proportion
of true second-order kin that will be lost below the threshold (i.e.,
the false-negative rate) based on the observed distribution of kin-pair
statistics. Only kin-pairs that are above the threshold will be treated
as HSPs, but the probability formula can be multiplied by the complement
of the false-negative probability to compensate. See \citet{bravington_close-kin_2016}
or \citet{Hillary2018WS-CKMR} for more details. The false-negative
rate depends both on the species and the genotyping method (in particular,
the number of loci) and cannot be predicted in advance, but experience
suggests that 15\% is usually a safe upper limit.

Determining that a pair is HSP does not differentiate between mHSPs
(maternal; shared mother) and pHSPs (paternal; shared father). This
can be determined by genotyping the mitochondrial DNA (mtDNA; always
inherited from the mother only) of known HSPs. If the genotypes are
different, the descent must be paternal; if the same, descent is probably
maternal, but could arise by chance in a few paternal-HSP cases. However,
in our experience, except for very small populations (hundreds of
adults), mtDNA diversity has always been high enough that shared-mtDNA
HSPs might as well be treated as definite mHSPs. We assume as much
here.

\pagebreak{}

\section{Adjustments for non-sparse sampling\label{appendix:Adjustments-for-non-sparse}}

Use of the pseudo-log-likelihood Hessian to approximate the inverse
variance is not strictly justified in a mathematical sense, because
the pairwise comparisons are not fully mutually independent. The ``sparse
sampling'' assumption of \citet{bravington_close-kin_2016}, which
underlies the use of the Hessian, is therefore not strictly justified;
this does not lead to bias in point estimates, but the Hessian-based
approximation is likely to underestimate the true variance somewhat.
Accordingly, we have made some simple adjustments to ``effective
sample size'' based on summaries of the simulated datasets. This
should be quite adequate for design purposes— since, in any case,
all our variance estimates have to be based on uncertain assumptions
about true parameter values— but a more detailed treatment may be
worthwhile when it comes to analysing the real data.

A general and comprehensive treatment of non-independence in CKMR
is beyond the scope of this paper. We restrict attention to some obvious
aspects for walrus that are easy to address. We consider the comparisons
in stages: SPs, then MOPs, then XmHSPs. We adjust set the effective
sample size for each stage based on recaptures from the preceding
stages in one simulated dataset, as follows:
\begin{itemize}
\item Sample sizes are initially taken from the simulated dataset (thus
allowing detailed breakdown of sample size by age, year, etc). All
available samples are used for SP comparisons.
\item If an individual is self-recaptured, only its final capture will be
used in MOP and XmHSP comparisons (i.e. duly adjusting the sample
sizes sample sizes for MOPs and XmHSPs, as well as the number of MOPs
etc found if that individual is involved).
\item Any Offspring $o$ identified in a MOP, will be excluded from XmHSP
comparisons (since $o$'s sibship with any other sample $i$ can be
deduced from the MOP results, based on whether $i$ is also an offspring
of $o$'s Mother).
\end{itemize}
This deals with the implications of one type of kinship for the others,
but does not deal with multiple recaptures within a kinship class
(e.g. an individual who is sampled 3 times; given that sample A matches
sample B, and B matches C, it is redundant to compare A with C). There
are simple ways to handle that with real datasets, as long as age
is known fairly accurately.

\pagebreak{}

\section{Model checking\label{sec:Model-checking}}

\input{model_checking.tex}

\pagebreak{}

\section{Additional results\label{sec:Additional-results}}

\selectlanguage{american}%
\begin{table}
\caption{Expected CVs on adult female survival, juvenile female survival, and
the proportion of adult females in breeding state 2 under different
demographic and sampling scenarios with and without the use of lethal
samples and CKMR.\label{tab:LH_Expected-CVs}}

\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
\begin{cellvarwidth}[t]
\centering
Demographic 

Scenario
\end{cellvarwidth} & \begin{cellvarwidth}[t]
\centering
Lethal 

Samples
\end{cellvarwidth} & \begin{cellvarwidth}[t]
\centering
Sampling 

Scenario
\end{cellvarwidth} & CKMR & \begin{cellvarwidth}[t]
\centering
Adult Female 

Survival
\end{cellvarwidth} & \begin{cellvarwidth}[t]
\centering
Juvenile Female 

Survival
\end{cellvarwidth} & \begin{cellvarwidth}[t]
\centering
P. Adult Female 

in State 2
\end{cellvarwidth}\tabularnewline
\hline 
\hline 
1 & No & 1 & Yes & 0.01 & 0.05 & 0.1\tabularnewline
\hline 
1 & No & 2 & Yes & 0.01 & 0.04 & 0.09\tabularnewline
\hline 
1 & No & 3 & Yes & 0.01 & 0.04 & 0.09\tabularnewline
\hline 
1 & No & 4 & Yes & 0.02 & 0.05 & 0.11\tabularnewline
\hline 
1 & No & 5 & Yes & 0.01 & 0.05 & 0.1\tabularnewline
\hline 
1 & No & 6 & Yes & 0.01 & 0.05 & 0.1\tabularnewline
\hline 
1 & No & 7 & Yes & 0.01 & 0.05 & 0.1\tabularnewline
\hline 
1 & Yes & 1 & Yes & 0.01 & 0.04 & 0.1\tabularnewline
\hline 
1 & Yes & 2 & Yes & 0.01 & 0.04 & 0.09\tabularnewline
\hline 
1 & Yes & 3 & Yes & 0.01 & 0.04 & 0.09\tabularnewline
\hline 
1 & Yes & 4 & Yes & 0.01 & 0.05 & 0.1\tabularnewline
\hline 
1 & Yes & 5 & Yes & 0.01 & 0.04 & 0.1\tabularnewline
\hline 
1 & Yes & 6 & Yes & 0.01 & 0.04 & 0.1\tabularnewline
\hline 
1 & Yes & 7 & Yes & 0.01 & 0.05 & 0.09\tabularnewline
\hline 
2 & No & 1 & Yes & 0.01 & 0.03 & 0.06\tabularnewline
\hline 
2 & No & 2 & Yes & 0.01 & 0.02 & 0.05\tabularnewline
\hline 
2 & No & 3 & Yes & 0.01 & 0.02 & 0.05\tabularnewline
\hline 
2 & No & 4 & Yes & 0.01 & 0.03 & 0.07\tabularnewline
\hline 
2 & No & 5 & Yes & 0.01 & 0.03 & 0.06\tabularnewline
\hline 
2 & No & 6 & Yes & 0.01 & 0.03 & 0.06\tabularnewline
\hline 
2 & No & 7 & Yes & 0.01 & 0.03 & 0.06\tabularnewline
\hline 
2 & Yes & 1 & Yes & 0.01 & 0.03 & 0.06\tabularnewline
\hline 
2 & Yes & 2 & Yes & 0.01 & 0.02 & 0.05\tabularnewline
\hline 
2 & Yes & 3 & Yes & 0.01 & 0.02 & 0.05\tabularnewline
\hline 
2 & Yes & 4 & Yes & 0.01 & 0.03 & 0.06\tabularnewline
\hline 
2 & Yes & 5 & Yes & 0.01 & 0.03 & 0.06\tabularnewline
\hline 
2 & Yes & 6 & Yes & 0.01 & 0.03 & 0.06\tabularnewline
\hline 
2 & Yes & 7 & Yes & 0.01 & 0.03 & 0.06\tabularnewline
\hline 
3 & No & 1 & Yes & 0.02 & 0.06 & 0.13\tabularnewline
\hline 
3 & No & 2 & Yes & 0.02 & 0.05 & 0.11\tabularnewline
\hline 
3 & No & 3 & Yes & 0.02 & 0.05 & 0.11\tabularnewline
\hline 
3 & No & 4 & Yes & 0.02 & 0.07 & 0.14\tabularnewline
\hline 
3 & No & 5 & Yes & 0.02 & 0.06 & 0.13\tabularnewline
\hline 
3 & No & 6 & Yes & 0.02 & 0.06 & 0.13\tabularnewline
\hline 
3 & No & 7 & Yes & 0.02 & 0.06 & 0.12\tabularnewline
\hline 
3 & Yes & 1 & Yes & 0.02 & 0.06 & 0.12\tabularnewline
\hline 
3 & Yes & 2 & Yes & 0.01 & 0.05 & 0.11\tabularnewline
\hline 
3 & Yes & 3 & Yes & 0.01 & 0.05 & 0.11\tabularnewline
\hline 
3 & Yes & 4 & Yes & 0.02 & 0.06 & 0.13\tabularnewline
\hline 
3 & Yes & 5 & Yes & 0.02 & 0.06 & 0.12\tabularnewline
\hline 
3 & Yes & 6 & Yes & 0.02 & 0.06 & 0.12\tabularnewline
\hline 
3 & Yes & 7 & Yes & 0.02 & 0.06 & 0.12\tabularnewline
\hline 
1 & No & 1 & No & 0.03 & 0.07 & 1.01\tabularnewline
\hline 
1 & No & 2 & No & 0.03 & 0.06 & 0.92\tabularnewline
\hline 
1 & No & 3 & No & 0.03 & 0.06 & 0.92\tabularnewline
\hline 
1 & No & 4 & No & 0.04 & 0.08 & 1.1\tabularnewline
\hline 
1 & No & 5 & No & 0.04 & 0.08 & 1.04\tabularnewline
\hline 
1 & No & 6 & No & 0.04 & 0.08 & 1.04\tabularnewline
\hline 
1 & No & 7 & No & 0.03 & 0.07 & 1\tabularnewline
\hline 
1 & Yes & 1 & No & 0.03 & 0.06 & 0.94\tabularnewline
\hline 
1 & Yes & 2 & No & 0.02 & 0.06 & 0.86\tabularnewline
\hline 
1 & Yes & 3 & No & 0.02 & 0.06 & 0.86\tabularnewline
\hline 
1 & Yes & 4 & No & 0.04 & 0.07 & 1.03\tabularnewline
\hline 
1 & Yes & 5 & No & 0.03 & 0.07 & 0.97\tabularnewline
\hline 
1 & Yes & 6 & No & 0.03 & 0.07 & 0.97\tabularnewline
\hline 
1 & Yes & 7 & No & 0.03 & 0.06 & 0.94\tabularnewline
\hline 
2 & No & 1 & No & 0.02 & 0.04 & 0.6\tabularnewline
\hline 
2 & No & 2 & No & 0.01 & 0.03 & 0.54\tabularnewline
\hline 
2 & No & 3 & No & 0.01 & 0.03 & 0.54\tabularnewline
\hline 
2 & No & 4 & No & 0.02 & 0.05 & 0.65\tabularnewline
\hline 
2 & No & 5 & No & 0.02 & 0.04 & 0.61\tabularnewline
\hline 
2 & No & 6 & No & 0.02 & 0.04 & 0.61\tabularnewline
\hline 
2 & No & 7 & No & 0.02 & 0.04 & 0.59\tabularnewline
\hline 
2 & Yes & 1 & No & 0.01 & 0.04 & 0.55\tabularnewline
\hline 
2 & Yes & 2 & No & 0.01 & 0.03 & 0.51\tabularnewline
\hline 
2 & Yes & 3 & No & 0.01 & 0.03 & 0.51\tabularnewline
\hline 
2 & Yes & 4 & No & 0.02 & 0.04 & 0.6\tabularnewline
\hline 
2 & Yes & 5 & No & 0.01 & 0.04 & 0.56\tabularnewline
\hline 
2 & Yes & 6 & No & 0.01 & 0.04 & 0.56\tabularnewline
\hline 
2 & Yes & 7 & No & 0.01 & 0.04 & 0.55\tabularnewline
\hline 
3 & No & 1 & No & 0.04 & 0.09 & 1.25\tabularnewline
\hline 
3 & No & 2 & No & 0.03 & 0.08 & 1.13\tabularnewline
\hline 
3 & No & 3 & No & 0.03 & 0.08 & 1.13\tabularnewline
\hline 
3 & No & 4 & No & 0.06 & 0.11 & 1.36\tabularnewline
\hline 
3 & No & 5 & No & 0.05 & 0.1 & 1.29\tabularnewline
\hline 
3 & No & 6 & No & 0.05 & 0.1 & 1.29\tabularnewline
\hline 
3 & No & 7 & No & 0.04 & 0.09 & 1.24\tabularnewline
\hline 
3 & Yes & 1 & No & 0.04 & 0.08 & 1.17\tabularnewline
\hline 
3 & Yes & 2 & No & 0.03 & 0.07 & 1.07\tabularnewline
\hline 
3 & Yes & 3 & No & 0.03 & 0.07 & 1.07\tabularnewline
\hline 
3 & Yes & 4 & No & 0.05 & 0.09 & 1.27\tabularnewline
\hline 
3 & Yes & 5 & No & 0.04 & 0.09 & 1.21\tabularnewline
\hline 
3 & Yes & 6 & No & 0.04 & 0.09 & 1.21\tabularnewline
\hline 
3 & Yes & 7 & No & 0.04 & 0.08 & 1.16\tabularnewline
\hline 
\end{tabular}
\end{table}

\begin{table}
\selectlanguage{english}%
\caption{Expected CV on adult female population size in 2015, 2020, and 2025
with different demographic and sampling scenarios and with and without
the use of lethal samples and CKMR. \label{tab:N_Expected-CV}}

\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
\begin{cellvarwidth}[t]
\centering
Demographic 

Scenario
\end{cellvarwidth} & \begin{cellvarwidth}[t]
\centering
Lethal 

Samples
\end{cellvarwidth} & \begin{cellvarwidth}[t]
\centering
Sampling 

Scenario
\end{cellvarwidth} & CKMR & \begin{cellvarwidth}[t]
\centering
2015 

Adult Females
\end{cellvarwidth} & \begin{cellvarwidth}[t]
\centering
2020 

Adult Females
\end{cellvarwidth} & \begin{cellvarwidth}[t]
\centering
2025 

Adult Females
\end{cellvarwidth}\tabularnewline
\hline 
\hline 
1 & No & 1 & Yes & 0.07 & 0.1 & 0.14\tabularnewline
\hline 
1 & No & 2 & Yes & 0.06 & 0.08 & 0.12\tabularnewline
\hline 
1 & No & 3 & Yes & 0.06 & 0.08 & 0.12\tabularnewline
\hline 
1 & No & 4 & Yes & 0.08 & 0.12 & 0.16\tabularnewline
\hline 
1 & No & 5 & Yes & 0.07 & 0.1 & 0.14\tabularnewline
\hline 
1 & No & 6 & Yes & 0.07 & 0.1 & 0.14\tabularnewline
\hline 
1 & No & 7 & Yes & 0.07 & 0.1 & 0.14\tabularnewline
\hline 
1 & Yes & 1 & Yes & 0.07 & 0.09 & 0.13\tabularnewline
\hline 
1 & Yes & 2 & Yes & 0.06 & 0.08 & 0.11\tabularnewline
\hline 
1 & Yes & 3 & Yes & 0.06 & 0.08 & 0.11\tabularnewline
\hline 
1 & Yes & 4 & Yes & 0.07 & 0.11 & 0.15\tabularnewline
\hline 
1 & Yes & 5 & Yes & 0.07 & 0.09 & 0.13\tabularnewline
\hline 
1 & Yes & 6 & Yes & 0.07 & 0.09 & 0.13\tabularnewline
\hline 
1 & Yes & 7 & Yes & 0.07 & 0.09 & 0.13\tabularnewline
\hline 
2 & No & 1 & Yes & 0.04 & 0.05 & 0.08\tabularnewline
\hline 
2 & No & 2 & Yes & 0.03 & 0.04 & 0.06\tabularnewline
\hline 
2 & No & 3 & Yes & 0.03 & 0.04 & 0.06\tabularnewline
\hline 
2 & No & 4 & Yes & 0.04 & 0.06 & 0.09\tabularnewline
\hline 
2 & No & 5 & Yes & 0.04 & 0.05 & 0.08\tabularnewline
\hline 
2 & No & 6 & Yes & 0.04 & 0.05 & 0.08\tabularnewline
\hline 
2 & No & 7 & Yes & 0.04 & 0.05 & 0.08\tabularnewline
\hline 
2 & Yes & 1 & Yes & 0.03 & 0.05 & 0.07\tabularnewline
\hline 
2 & Yes & 2 & Yes & 0.03 & 0.04 & 0.06\tabularnewline
\hline 
2 & Yes & 3 & Yes & 0.03 & 0.04 & 0.06\tabularnewline
\hline 
2 & Yes & 4 & Yes & 0.04 & 0.05 & 0.08\tabularnewline
\hline 
2 & Yes & 5 & Yes & 0.03 & 0.05 & 0.07\tabularnewline
\hline 
2 & Yes & 6 & Yes & 0.03 & 0.05 & 0.07\tabularnewline
\hline 
2 & Yes & 7 & Yes & 0.03 & 0.05 & 0.07\tabularnewline
\hline 
3 & No & 1 & Yes & 0.09 & 0.13 & 0.18\tabularnewline
\hline 
3 & No & 2 & Yes & 0.08 & 0.11 & 0.15\tabularnewline
\hline 
3 & No & 3 & Yes & 0.08 & 0.11 & 0.15\tabularnewline
\hline 
3 & No & 4 & Yes & 0.1 & 0.15 & 0.21\tabularnewline
\hline 
3 & No & 5 & Yes & 0.09 & 0.13 & 0.18\tabularnewline
\hline 
3 & No & 6 & Yes & 0.09 & 0.13 & 0.18\tabularnewline
\hline 
3 & No & 7 & Yes & 0.09 & 0.13 & 0.18\tabularnewline
\hline 
3 & Yes & 1 & Yes & 0.08 & 0.12 & 0.17\tabularnewline
\hline 
3 & Yes & 2 & Yes & 0.08 & 0.1 & 0.14\tabularnewline
\hline 
3 & Yes & 3 & Yes & 0.08 & 0.1 & 0.14\tabularnewline
\hline 
3 & Yes & 4 & Yes & 0.09 & 0.14 & 0.19\tabularnewline
\hline 
3 & Yes & 5 & Yes & 0.09 & 0.12 & 0.17\tabularnewline
\hline 
3 & Yes & 6 & Yes & 0.09 & 0.12 & 0.17\tabularnewline
\hline 
3 & Yes & 7 & Yes & 0.08 & 0.12 & 0.17\tabularnewline
\hline 
1 & No & 1 & No & 0.14 & 0.19 & 0.31\tabularnewline
\hline 
1 & No & 2 & No & 0.14 & 0.15 & 0.23\tabularnewline
\hline 
1 & No & 3 & No & 0.14 & 0.15 & 0.23\tabularnewline
\hline 
1 & No & 4 & No & 0.15 & 0.25 & 0.42\tabularnewline
\hline 
1 & No & 5 & No & 0.15 & 0.21 & 0.34\tabularnewline
\hline 
1 & No & 6 & No & 0.15 & 0.21 & 0.34\tabularnewline
\hline 
1 & No & 7 & No & 0.14 & 0.19 & 0.31\tabularnewline
\hline 
1 & Yes & 1 & No & 0.14 & 0.17 & 0.27\tabularnewline
\hline 
1 & Yes & 2 & No & 0.13 & 0.14 & 0.21\tabularnewline
\hline 
1 & Yes & 3 & No & 0.13 & 0.14 & 0.21\tabularnewline
\hline 
1 & Yes & 4 & No & 0.14 & 0.21 & 0.36\tabularnewline
\hline 
1 & Yes & 5 & No & 0.14 & 0.19 & 0.3\tabularnewline
\hline 
1 & Yes & 6 & No & 0.14 & 0.19 & 0.3\tabularnewline
\hline 
1 & Yes & 7 & No & 0.13 & 0.17 & 0.27\tabularnewline
\hline 
2 & No & 1 & No & 0.06 & 0.09 & 0.15\tabularnewline
\hline 
2 & No & 2 & No & 0.06 & 0.07 & 0.11\tabularnewline
\hline 
2 & No & 3 & No & 0.06 & 0.07 & 0.11\tabularnewline
\hline 
2 & No & 4 & No & 0.07 & 0.12 & 0.2\tabularnewline
\hline 
2 & No & 5 & No & 0.07 & 0.1 & 0.16\tabularnewline
\hline 
2 & No & 6 & No & 0.07 & 0.1 & 0.16\tabularnewline
\hline 
2 & No & 7 & No & 0.06 & 0.09 & 0.15\tabularnewline
\hline 
2 & Yes & 1 & No & 0.06 & 0.08 & 0.13\tabularnewline
\hline 
2 & Yes & 2 & No & 0.06 & 0.07 & 0.1\tabularnewline
\hline 
2 & Yes & 3 & No & 0.06 & 0.07 & 0.1\tabularnewline
\hline 
2 & Yes & 4 & No & 0.06 & 0.1 & 0.17\tabularnewline
\hline 
2 & Yes & 5 & No & 0.06 & 0.09 & 0.14\tabularnewline
\hline 
2 & Yes & 6 & No & 0.06 & 0.09 & 0.14\tabularnewline
\hline 
2 & Yes & 7 & No & 0.06 & 0.08 & 0.13\tabularnewline
\hline 
3 & No & 1 & No & 0.19 & 0.25 & 0.41\tabularnewline
\hline 
3 & No & 2 & No & 0.18 & 0.2 & 0.31\tabularnewline
\hline 
3 & No & 3 & No & 0.18 & 0.2 & 0.31\tabularnewline
\hline 
3 & No & 4 & No & 0.2 & 0.33 & 0.56\tabularnewline
\hline 
3 & No & 5 & No & 0.19 & 0.28 & 0.45\tabularnewline
\hline 
3 & No & 6 & No & 0.19 & 0.28 & 0.45\tabularnewline
\hline 
3 & No & 7 & No & 0.19 & 0.25 & 0.42\tabularnewline
\hline 
3 & Yes & 1 & No & 0.18 & 0.23 & 0.36\tabularnewline
\hline 
3 & Yes & 2 & No & 0.18 & 0.19 & 0.28\tabularnewline
\hline 
3 & Yes & 3 & No & 0.18 & 0.19 & 0.28\tabularnewline
\hline 
3 & Yes & 4 & No & 0.19 & 0.28 & 0.47\tabularnewline
\hline 
3 & Yes & 5 & No & 0.19 & 0.25 & 0.41\tabularnewline
\hline 
3 & Yes & 6 & No & 0.19 & 0.25 & 0.41\tabularnewline
\hline 
3 & Yes & 7 & No & 0.18 & 0.22 & 0.36\tabularnewline
\hline 
\end{tabular}\selectlanguage{english}%
\end{table}
\selectlanguage{english}%

