\selectlanguage{american}%

Estimation of abundance and of other demographic parameters such as
survival is a key part of wildlife management and conservation. Traditional
mark-recapture analysis \citep{williams_analysis_2002} can deliver
estimates with low bias and uncertainty, provided that enough individual
animals i) are naturally, artificially, or genetically “marked” and
identifiable and ii) can be recaptured over time. If genotypes are
used as the marks, as in genetic individual mark-recapture (IMR; \citealp{palsboll_genetic_1997}),
then kinship patterns amongst the samples (parents, siblings, etc)
contains additional information relevant to demographics \citep{skaug_allele-sharing_2001}.
Close-kin mark-recapture (CKMR; see \citealp{bravington_close-kin_2016})
is a framework for using these kinships, as inferred from genotypes,
to estimate abundance and demographic parameters. CKMR provides additional
flexibility compared with IMR since lethal samples (from sampling,
hunting, natural mortality etc.) and/or non-lethal samples can be
used; it also increases the effective sample size, since more types
of ``recapture'' are possible. As of 2025, most CKMR projects have
been for commercial fish (e.g., \citealp{Davies2020SBT2}) or sharks
(e.g., \citealp{Hillary2018WS-CKMR}), but there are also some for
mammals, including \citet{conn_robustness_2020}'s modeling study
of bearded seals and its implementation by \citet{taras_estimating_2024},
and \citet{lloyd-jones_close-kin_2023} for flying foxes.

The principle behind CKMR is that every individual has (or had) one
mother and one father; thus, for a given sample size, in a large population
there will be few ``recaptures'' of parents or their other descendants,
while in a small population there will be many. In practice, the data
for CKMR comprise the outcome of pairwise kinship checks amongst samples,
plus covariates associated with each sample such as its date of capture,
age, size, sex etc. The CKMR model has two components: a population-dynamics
part driven by the demographic parameters; and formulae for the expected
frequencies of different kinship types in pairwise comparisons, conditional
on sample covariates and population dynamics. By combining the kinship
data with the model, parameters can be estimated using maximum-likelihood
or Bayesian methods.

CKMR has mostly been used in situations where self-recaptures are
unlikely or impossible (e.g., because sampling is lethal). \citet{lloyd-jones_close-kin_2023}
did include IMR results in a CKMR study but did not integrate both
datasets into a single model. Here, we focus on a population where
IMR was the original project goal; therefore we extend traditional
CKMR to include IMR in the same model as an additional kinship type,
whereby pairwise genetic comparison can show that two samples are
from the same animal.

The success of CKMR and/or IMR depends on whether data collected contain
sufficient recaptures. Sampling design (e.g. number of samples, composition,
study duration, type and quality of covariate measurements) is crucial
to avoid expensive, embarrassing, and predictable failure. The pairwise-comparison
framework leads to analytical results for expected number of kin-pairs
and expected variance given expected number of samples (and associated
covariates), so that simulation is not essential; nevertheless, simulation
can be useful as a way to check the fairly complex code of kinship
probabilities and design setup. In this paper we show how to do and
check the calculations using a case study on the Pacific walrus (\emph{Odobenus
rosmarus divergens}; hereafter, walrus) in the North Pacific. We explore
different demographic and design scenarios for walrus using IMR alone
versus CKMR + IMR = ICKMR, and demonstrate how the latter can be used
to substantially reduce the overall amount of survey effort required
for adequate monitoring.

In the rest of this Introduction, we provide some background on CKMR
(drawn from \citealt{bravington_close-kin_2016} and experience on
projects since), and on walrus biology and the survey setup. In Methods,
we describe our walrus population dynamics model, derive walrus-appropriate
kinship probability formulae, and show how to analytically calculate
the expected variances that might come from different survey designs.
We also outline the simulation setup which we used to test our ICKMR
model. The Results section shows how different survey designs are
likely to perform (e.g., with\slash without CKMR). In the Discussion,
we summarize our conclusions for walrus, and also mention some modeling
simplifications made for design purposes that we may wish to reconsider
when working with real data.

\subsection{Walrus biology and background}

The walrus is a gregarious, ice-associated pinniped inhabiting continental
shelf waters of the Bering and Chukchi seas. During winter (when sea
ice forms south of the Bering Strait) virtually all walruses occupy
the Bering Sea \citep{fay_ecology_1982}. In summer (when sea ice
is absent from the Bering Sea) almost all juvenile and adult female
walruses, and some adult male walruses, migrate north to the Chukchi
Sea. When walruses rest offshore on sea ice floes, their distribution
is dynamic, because it generally follows the marginal ice zone (a
moving, changing habitat which contains a mix of ice floes and water)
but also concentrates in regions of high benthic productivity. This
allows walruses to forage for benthic invertebrates while simultaneously
having access to a nearby substrate for hauling out.

{*}{*}{*}NEED something about walrus moving about all over the place,
from IMR data and (more likely) sat tags :) Some of that {*}could{*}
go to the Discussion, but I think at least a pre-mention here, coz
it will otherwise be in the alert reader's mind as they look at the
model structure

{*}{*}{*}Walrus reprod biol summary could go here? Rather than putting
it off until Methods. See sec 2.1

Sea ice has declined for decades \citep{perovich_loss_2009,stroeve_trends_2012,stroeve_changing_2018},
and coupled global atmospheric-ocean general circulation models predict
its continued decline \citep{arthun_seasonal_2021}. When sea ice
recedes from the continental shelf, walruses come on shore to rest
in large herds at sites termed haulouts, from which they make long
trips to foraging hotspots \citep{jay_walrus_2012}. This change in
their activity budgets \citep{jay_walrus_2017} may ultimately lead
to a decline in body condition and an increase in mortality or a decrease
in reproduction \citep{udevitz_forecasting_2017}. Furthermore, disturbance
at haulouts can cause stampedes, resulting in mass calf and juvenile
mortality. Continued sea-ice loss and a concomitant increase in the
intensity and expansion of industrial and shipping activities in Pacific
Arctic waters \citep{silber_vessel_2019} are expected to drive a
substantial population decline \citep{garlich-miller_status_2011,maccracken_final_2017,johnson_assessing_2023,johnson_assessing_2024}.

Range-wide abundance and demographic rate estimates are crucial for
understanding population status, as well as for developing and implementing
harvest management plans. In particular, subsistence walrus harvests
in Alaska and Chukotka exceed 4,000 animals annually (USFWS, 2023),
and indigenous peoples need information on the status of the walrus
population in order to manage these harvests sustainably. Furthermore,
in the United States, the Marine Mammal Protection Act (MMPA) requires
a determination of potential biological removal for walrus, which
in turn, requires a precise abundance estimate \citep{gilbert_review_1999,wade_determining_1999}.

Scientists have attempted to ascertain walrus population size since
at least 1880 \citep{fay_managing_1989}, and until very recently,
unsuccessfully. The most concerted effort was the 1975-2006 range-wide
airplane-based surveys conducted collaboratively with the Soviet Union
and then Russian Federation. However, resulting estimates were biased
and imprecise, and count-based methods were abandoned after the 2006
survey which, despite a rigorous design, innovative field methods,
and sophisticated analyses, yielded a 95\% confidence interval (CI)
on the population size estimate of 55,000–507,000 animals (CV = 0.93).
The extensive imprecision in the estimate resulted from the walrus
population being widely dispersed with unpredictable local clumping
\citep{speckman_results_2011,jay_walrus_2012}, which is, in turn,
due to the large area of arctic and subarctic continental shelf over
which they forage, their gregarious nature, and the dynamic nature
of the marginal ice zone.

The first rigorous walrus survival rate estimates were obtained within
the past decade via Bayesian integrated population models (IPMs),
which combined multiple data sources to estimate demographic rates
and population trend over multiple decades \citep{taylor_demography_2015,taylor_demography_2018}.
However, the original problems with the aerial survey data continued
to preclude conclusions about population abundance in the IPMs \citep{taylor_demography_2015}.

In 2013, the U.S. Fish and Wildlife Service (FWS) initiated a genetic
IMR project to estimate walrus abundance and demographic rates. Under
this approach, genetic ``marking'' via skin biopsy samples \citep{palsboll_genetic_1997}
provided a major advantage over traditional marking techniques because
walruses are extremely difficult to handle physically. Over five years
of research cruises, biologists attempted to collect a representative
sample of walruses in the accessible portion of the marginal ice zone
in each year a cruise was conducted, although Russian waters were
not accessible in all years. Sampling focused on groups of adult females
and juveniles, as these classes are the demographically important
population segments of this polygynous species \citep{fay_ecology_1982}.
Further methods for the IMR study are detailed by Beatty et al. (\cite*{beatty_panmixia_2020,beatty_estimating_2022}).

Data analysis from the first generation of walrus research cruises
(2013–2017) used a Cormack-Jolly-Seber multievent model to estimate
survival rates, and a Horvitz-Thompson-like estimator to obtain population
size. The total abundance of 257,000 had a 95\% credible interval
(CrI) of 171,000–366,000 (CV=0.19; \citealt{beatty_estimating_2022}).
Although the precision of the abundance estimate from the IMR study
was much improved over the final aerial survey, the IMR study required
extensive investment of human and financial resources (i.e, USD \$5,000,000).
A more cost-effective approach is needed to assess the walrus population
on a regular interval. As mentioned above, biopsy samples also contain
information about kin relationships, which, through CKMR, can substantially
augment the information content of genetic IMR without increasing
sampling effort. {[}1526 words{]}.\selectlanguage{english}%

